Results

### 2017-11-28 tmp-results.Rmd
save

# Put all results in a single tibble
results <- list.files("results1", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  as_tibble() %>%
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all"))),
    AUC = map_dbl(eval, ~bigstatsr::AUC(.x[, 1], .x[, 2])),
    percCases10 = map_dbl(eval, ~mean(.x[order(.x[, 1], decreasing = TRUE)[top10], 2])),
    percCases20 = map_dbl(eval, ~mean(.x[order(.x[, 1], decreasing = TRUE)[top20], 2]))
  )
```

```{r}
results %>%
  filter(method %in% c("T-Trees", "logit-simple")) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise_at(c("timing", "nb.preds", "AUC", "percCases10", "percCases20"), mean) %>%
  print(n = Inf)
```

```{r, fig.width=16, out.width="95%", dev="svg", fig.cap="Results of T-Trees vs penalized logistic regression. **A.** Timing (in seconds). **B.** Number of predictors of the model. **C.** AUC. **D.** Percentage of cases in the 10% largest scores."}
ttrees_vs_logit <- filter(results, method %in% c("T-Trees", "logit-simple"))

@@

```{r, fig.cap="AUC as function of M. For all chromosomes."}
results2 %>%
  filter(
    # method %in% c("logit-simple", "PRS-max"),
    grepl("all", par.causal)
  ) %>%
  mutate(M = readr::parse_number(par.causal)) %>%
  group_by(M, par.dist, par.h2, par.model, method) %>%
  summarise(AUC = mean(AUC)) %>%
  # filter(par.h2 == 0.8, par.dist == "gaussian", par.model == "simple") %>%
  filter(par.h2 == 0.8) %>%
  myggplot(aes(M, AUC, color = method)) +
  geom_line() + 
  geom_point(size = 2) +
  facet_grid(par.dist ~ par.model) +
  scale_y_continuous(breaks = 0:10 / 10, minor_breaks = c(0:9 + 0.5) / 10) +
  scale_x_sqrt(breaks = c(30, 300, 1200, 3000)) +
  labs(x = "Number of causal SNPs (sqrt-scale)")
```

```{r, fig.cap="AUC as function of M. For chromosome 6."}
results3 %>%
  filter(
    # method %in% c("logit-simple", "PRS-max"),
    grepl("all", par.causal)
  ) %>%
  mutate(M = readr::parse_number(par.causal)) %>%
  group_by(M, par.dist, par.h2, par.model, method) %>%
  summarise(AUC = mean(AUC)) %>%
  # filter(par.h2 == 0.8, par.dist == "gaussian", par.model == "simple") %>%
  filter(par.h2 == 0.8) %>%
  myggplot(aes(M, AUC, color = method)) +
  geom_line() + 
  geom_point(size = 2) +
  facet_grid(par.dist ~ par.model) +
  scale_y_continuous(breaks = 0:10 / 10, minor_breaks = c(0:9 + 0.5) / 10) +
  scale_x_sqrt(breaks = c(30, 300, 1200, 3000)) +
  labs(x = "Number of causal SNPs (sqrt-scale)")
```

>>>>

# Put all results in a single tibble
results1 <- list.files("results1", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  as_tibble() %>%
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all"))),
    AUC = map_dbl(eval, ~bigstatsr::AUC(.x[, 1], .x[, 2])),
    percCases10 = map_dbl(eval, ~mean(.x[order(.x[, 1], decreasing = TRUE)[top10], 2])),
    percCases20 = map_dbl(eval, ~mean(.x[order(.x[, 1], decreasing = TRUE)[top20], 2]))
  )
```

```{r}
results1 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise_at(c("timing", "nb.preds", "AUC", "percCases10", "percCases20"), mean) %>%
  print(n = Inf)
```

```{r, fig.width=16, out.width="95%", dev="svg", fig.cap="Results of T-Trees vs penalized logistic regression. **A.** Timing (in seconds). **B.** Number of predictors of the model. **C.** AUC. **D.** Percentage of cases in the 10% largest scores."}
ttrees_vs_logit <- filter(results1, method %in% c("T-Trees", "logit-simple"))

@@
